Analyzing X-ray images in Python with scikit-image

### 2016-08-20 skimage_tomo.tex
Update abstract/intro

\begin{abstract} % abstract
    The exploration and processing of images is a vital aspect of the
    scientific workflow of different X-ray imaging modalities. Users
    require tools combining interactivity, versatility, and performance.

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language, that supports a large variety of file formats
    and is compatible with 2-D and 3-D images. The toolkit exposes a
    simple programming interface, corresponding to functions performing
    operations on images, and different thematic modules that group these
    functions according to their purpose, such as image restoration,
    segmentation, measurements, etc. \texttt{scikit-image} users benefit
    from the rich ecosystem of Python for science, with powerful
    visualization libraries or machine learning toolkits.
    \texttt{scikit-image} combines a gentle
    learning curve, versatile image processing capabilities, and the
    scalable performances required for the high-throughput analysis of
    X-ray imaging data.

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community \citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers \citep{pytango}, to access raw data of X-ray
detectors \citep{Knudsen2013}, to reconstruct tomography volumes from
radiographs \citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography \citep{Adams2010},
azimuthal integration of diffraction data \citep{Ashiotis2015} or
fluorescence analysis \citep{pymca}.

>>>>

\begin{abstract} % abstract
    The exploration and processing of images is a vital aspect of the
    scientific workflows of many X-ray imaging modalities. Users
    require tools that combine interactivity, versatility, and performance.

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language that supports a large variety of file formats
    and is compatible with 2-D and 3-D images. The toolkit exposes a
    simple programming interface for functions that perform various
    operations on images, grouped thematically according to their
    purpose, e.g. image restoration,
    segmentation, measurements, etc. \texttt{scikit-image} users benefit
    from a rich scientific Python ecosystem that contains many
    powerful libraries for tasks such as visualization or machine learning.
    \texttt{scikit-image} provides a gentle
    learning curve, versatile image processing capabilities, and the
    scalable performances required for the high-throughput analysis of
    X-ray imaging data.

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community \citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- thereby
limiting the complexity of the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers \citep{pytango}, to access raw data of X-ray
detectors \citep{Knudsen2013}, to reconstruct tomography volumes from
radiographs \citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography \citep{Adams2010},
azimuthal integration of diffraction data \citep{Ashiotis2015} or
fluorescence analysis \citep{pymca}.
